%!TeX program = pdflatex
% Lan Peng's Curriculum Vitae
% Email: lanpeng@buffalo.edu
% The original templete of this CV is modified and adopted from: https://github.com/gboeing/cv

\documentclass[12pt,letterpaper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) for accented characters as single glyph
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % regionalize hyphens, quote marks, etc automatically
\usepackage{microtype}% improve text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto}    % make nice tabbing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts
\usepackage{setspace} % custom line spacing

% what is your name?
\newcommand{\myname}{Lan Peng}

% select default typefaces
\usepackage{ebgaramond} % document's serif typeface
\usepackage{helvet}     % document's sans serif typeface

% how far to tab for list items with left-aligned date: different fonts need different widths
\newcommand{\listtabwidth}{1.7cm}

% define font to use as document's title
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*, family=\sfdefault}{30} % increase sans serif headings tracking
\titleformat{\section}{\lsstyle\sffamily\small\bfseries\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{25pt plus 4pt minus 4pt}{8pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\lsstyle\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{16pt plus 4pt minus 4pt}{4pt plus 2pt minus 2pt}

% set page margins (assumes letter paper)
\geometry{body={6.5in, 9.0in},
    left=1.0in,
    top=1.0in}

% prevent paragraph indentation
\setlength\parindent{0em}

% set line spacing
\setstretch{0.9}

% define space between list items
\newcommand{\listitemspace}{0.25em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
                \setlength{\parskip}{0em}
                \setlength{\itemsep}{\listitemspace}
                \setlength{\parsep}{\listitemspace}}}
{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print only the month and year when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    citecolor   = black,
    linkcolor   = black,
    pdfauthor   = {\myname},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\begin{document}
    \raggedright{}

    % display your name as the document title
    \namefont{\myname}

    % affiliation and contact info blocks
    \vspace{1em}
    \begin{minipage}[t]{0.700\textwidth}
        % current primary affiliation, left-aligned
        \textbf{Ph.D. Candidate} \\
        Department of Industrial and Systems Engineering \\
        School of Engineering and Applied Sciences \\
        University at Buffalo, State University of New York
    \end{minipage}
    \begin{minipage}[t]{0.295\textwidth}
        % contact info details, right-aligned
        \flushright{}
        \quad\\
        \href{lanpeng@buffalo.edu}{lanpeng@buffalo.edu} \\
        +1 716 603 1327 \\
        \href{https://github.com/isaac0821}{github.com/isaac0821}
    \end{minipage}

    % \noindent\rule[0\baselineskip]{\textwidth}{1pt}

    \section*{Education}
    \begin{tablist}
        \item[Ph.D.]  \tab{}Industrial Engineering, Operations Research \tab{}Department of Industrial and Systems Engineering, University at Buffalo, SUNY \tab{}2018 - In progress (Expected Dec. 2022)
        \item[M.S.]  \tab{}Industrial Engineering, Operations Research, \tab{}Department of Industrial and Systems Engineering, University at Buffalo, SUNY \tab{}2018 - 2020
        \item[M.S.]  \tab{}Control Science and Engineering, \tab{}School of Reliability and Systems Engineering, Beihang University, \tab{}2015 - 2018
        \item[B.S.]  \tab{}Quality and Reliability Engineering, \tab{}School of Reliability and Systems Engineering, Beihang University, \tab{}2011 - 2015
        % \item[High School] \tab{}Xiamen Foreign Language School, 2005 - 2011
    \end{tablist}

    \section*{Research Areas}
    \begin{itemize}
        \item Vehicle Routing Problem: Drone Delivery, Dynamic Vehicle Routing Problem
    \end{itemize}

    \section*{Publications}
    $^\dagger$ Advisor
    \subsection*{Journal Articles}
    \begin{tablist}
        \item[J1] \tab{}\textbf{Peng, Lan.}, and Murray, Chase$^\dagger$. \enquote{VeRoViz: A vehicle routing visualization toolkit.} \textit{INFORMS Journal on Computing}, published online. 2022. \href{https://pubsonline.informs.org/doi/abs/10.1287/ijoc.2022.1159}{https://doi.org/10.1287/ijoc.2022.1159}
    \end{tablist}

    \subsection*{Manuscripts In Preparation}
    \begin{tablist}
    \item[] \tab{}\textbf{Peng, Lan.}, and Murray, Chase$^\dagger$. \enquote{Parallel Drone Scheduling Traveling Salesman Problem with Weather Impacts.} \textit{To be submitted.}
    \item[] \tab{}\textbf{Peng, Lan.}, and Murray, Chase$^\dagger$. \enquote{The Dynamic Pickup-and-Delivery Bundling Problem.} \textit{To be submitted.}
    \item[] \tab{}\textbf{Peng, Lan.}, and Murray, Chase$^\dagger$. \enquote{Staffing Optimization in Parallel Drone Scheduling Traveling Salesman Problem with Weather Impacts.} \textit{In preparation.}
    \end{tablist}

    \subsection*{Conference Proceedings}
    \begin{tablist}        
        \item[C2] \tab{}\textbf{Peng, Lan.}, Ma, Lin$^\dagger$., and Naichao, Wang.\enquote{A fleet-level selective maintenance model for long-distance highway transportation considering stochastic repair quality.} \textit{2017 2nd International Conference on System Reliability and Safety (ICSRS)} (EI). Milan, Italy. 2017. \href{https://ieeexplore.ieee.org/abstract/document/8272847}{https://ieeexplore.ieee.org/abstract/document/8272847}
        \item[C1] \tab{}\textbf{Peng, Lan.}, Liu, Baocheng., Ma, Lin$^\dagger$., Naichao, Wang. and Liu, Qiannan.\enquote{Mixed arithmetic reduction model for two-unit system maintenance} \textit{2017 Second International Conference on Reliability Systems Engineering (ICRSE)} (EI). Beijing, China. 2017. \href{https://ieeexplore.ieee.org/abstract/document/8030798}{https://ieeexplore.ieee.org/abstract/document/8030798}

    \end{tablist}

    \section*{Dissertations}
    \begin{tablist}
        \item[\the\year] \tab{} Ph.D. Thesis. \enquote{Emerging Topics in Coordinated Vehicle Routing Problem: Application from Last-Mile Drone Delivery to Nation-wide Bulk Item Shipping}
        \item[2018] \tab{} Master Thesis. \enquote{Maintenance policy for multi-unit system considering negative repair performance} (In Chinese)
    \end{tablist}

    \section*{Presentation}
    \subsection*{Conference Presentation}
    \begin{tablist}
        \item[3.] \tab{}\textbf{Peng, Lan.}, and Murray, Chase$^\dagger$. \enquote{Parallel Drone Scheduling Traveling Salesman Problem with Weather Impacts.} \textit{INFORMS Annual Meeting}. Virtual, Nov. 2021.
        \item[2.] \tab{}\textbf{Peng, Lan.}, and Murray, Chase$^\dagger$. \enquote{Optimization Of Pick-up And Delivery Orders Bundling Problem.} \textit{INFORMS Annual Meeting}. Virtual, Nov. 2020.
        \item[1.] \tab{}Murray, Chase$^\dagger$., and \textbf{Peng, Lan.} \enquote{A Vehicle Routing Visualization Toolkit for Drones.} \textit{INFORMS Annual Meeting}. Seattle, WA, U.S., Oct. 2019.
    \end{tablist}

    \section*{Research Experience}
    \subsection*{Dissertation, University at Buffalo}
    \begin{tablist}
        \item[2021 - $\sim$] \tab{} ``Drone Delivery Considering Weather Impacts''
        \item \tab{} Research Problem: A fleet of drones and a truck deliver packages in parallel; the truck leaves the depot and visits customers in sequence, while drones fly between the depot and customers and deliver to customers one at a time. The winds and precipitation impact the operation of drones - the energy consumption rate changes according to wind speed and payload; also, moving no-fly zones are modeled to simulate rainfall. In this research, the optimization of staff configuration is also investigated - to minimize the long-term personnel costs increased due to the deviation of work hours because of weather variation.
    \end{tablist}
    \subsection*{Dissertation, University at Buffalo}
    \begin{tablist}
        \item[2020 - $\sim$] \tab{} ``Dynamic Pickup and Delivery Bundling Problem''
        \item \tab{} Research Problem: An online car dealership is moving inventories nationwide. When an inventory is set up for delivery, a request will be posted online for moving companies to take the order. In this research, the car dealership will bundle the delivery requests in which the origin or destination are close, considering the moving companies will accept bundles only if they are interested. Delivery requests arrive with a time-dependent arrival rate throughout the day, and all need to be posted within a specific time limit. The objective is to create attractive bundles among delivery requests and optimize the policy of deciding the timing for the requests to wait to be bundled.
    \end{tablist}

    \subsection*{Research Assistant, University at Buffalo}
    \begin{tablist}
        \item[2019] \tab{} \textit{ACV Auctions, Inc.} (Online B2B car dealership)\\
        \item[] \tab{} Develop web-based toolkit for graphical view of available inventory. 
        \item[] \tab{} Develop algorithm for optimizing the bundle generation of pickup-and-delivery requests in dynamic environment.
    \end{tablist}

    \section*{Teaching Experience}
    \subsection*{Teaching Assistant, University at Buffalo}
    \begin{tablist}
        \item[2018] \tab{} IE 320 \ Engineering Economy
        \item[2019] \tab{} IE 374 \ System Modeling and Operations Research II
        \item[2020] \tab{} IE 411/511 \ Social Network Behavior Models
        \item[2020] \tab{} IE 550/STL 502 \ Introduction to Operations Research
        \item[2021] \tab{} IE 101 \ Introduction to Industrial Engineering
        \item[2021] \tab{} IE 691 \ Research Seminar
        \item[2021] \tab{} IE 550/STL 502 \ Introduction to Operations Research
        \item[2021] \tab{} IE 677 \ Network Optimization
        \item[2022] \tab{} IE 421/521 \ Sustainable Manufacturing
        \item[2022] \tab{} IE 555 \ Programming for Analytics
    \end{tablist}

    \section*{Memberships}
    \begin{itemize}
        \item INFORMS Student Member\\
        \quad Served as Vice President for the University at Buffalo Student Chapter from 2020 - 2022
    \end{itemize}

    \section*{Skills}
    \begin{itemize}
        \item Language: Chinese (Native), English (Working proficiency)
        \item Programming: Python, C\#, JavaScript, HTML/CSS, SQL
        \item Software: Gurobi, CPLEX, LaTeX, PostgreSQL
    \end{itemize}

    \section*{PhD-Level Courses}
    \begin{tablist}
        \item[A] \tab{}IE 572 \ Linear Programming
        \item[A] \tab{}IE 575 \ Stochastic Methods
        \item[A] \tab{}IE 582 \ Robotic Systems
        \item[A] \tab{}IE 573 \ Discrete Optimization
        \item[A] \tab{}IE 576 \ Applied Stochastic Process
        \item[A] \tab{}IE 670 \ Topics in Operations Research (Data Visualization)
        \item[A-]\tab{}CSE 522 \ Object Oriented Design
        \item[A] \tab{}IE 671 \ Nonlinear Programming
        \item[A] \tab{}IE 677 \ Network Optimization
        \item[A] \tab{}CSE 531 \ Algorithms Analysis and Design I
        \item[A] \tab{}GEO 597 \ Geostatistics
        \item[A] \tab{}IE 670 \ Topics in Operations Research (Simulation)
        \item[A] \tab{}IE 670 \ Topics in Operations Research (Heuristic Optimization)
        \item[A] \tab{}IE 670 \ Topics in Operations Research (Logistics Optimization)
        \item[A] \tab{}IE 670 \ Topics in Operations Research (Urban Transportation Systems)
        \item[A] \tab{}IE 504 \ Facilities Design
    \end{tablist}

    \let\thefootnote\relax\footnote{Updated \monthyeardate\today}

\end{document}